The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2016-01-04 article.tex
The new aromaticity framework should be discussed too
Paragraph on signatures and two references

@@

>>>>

  \subsection*{Signatures}
  An implementation has been provided of the Signature structure descriptor for molecules 
  \cite{Faulon2003}. These act as a linear notation - like the SMILES format - 
  for the whole molecule as well as for connected substructures rooted at a single atom. The 
  descriptor can also be canonicalized to provide isomorphism-independent representations 
  \cite{Faulon2004}.

@@

  \subsubsection*{Aromaticity}
